---
title: "MFG_draft"
author: "Namuhan"
date: "2025-03-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "R:/HBMSC2022-A7264/")
```

```{r message=FALSE}
library(Seurat)
library(dplyr)
library(scCustomize)
library(ggplot2)
library(pdist)
library(edgeR)
library(biomaRt)
library(Scissor)
library(mclust)
```


# Preprocess Lemay dataset
We only work with 4 washed and matrue stage samples: SRR801700, SRR801702, SRR801703, and SRR801704 

## Create raw gene count matrix and convert gene ids to gene symbols
```{r}
filepath <- paste0("R:/HBMSC2022-A7264/51_MFG_draft/datasets/lemay/SRR801",c(700, 702, 703, 704),".tabular")

df <- lapply(filepath, read.table)
df <- data.frame(df)
genecount <- df[2:nrow(df),c(2, 4, 6, 8)]
colnames(genecount) <- paste0("Lemay_s", 1:4)
geneid <- df[2:nrow(df),1]
rownames(genecount) <- geneid

genes <- getBM(attributes = c('ensembl_gene_id_version', 'hgnc_symbol'),
               filters = 'ensembl_gene_id_version',
               values = geneid,
               mart = useEnsembl(biomart = "genes", 
                                 dataset = "hsapiens_gene_ensembl",
                                 version="GRCh37"))
genes <- genes[genes$hgnc_symbol!="",]

genes.left <- genes[!genes$hgnc_symbol %in% genes$hgnc_symbol[duplicated(genes$hgnc_symbol)],]
genes.left <- genes.left[!genes.left$ensembl_gene_id_version %in% genes$ensembl_gene_id_version[duplicated(genes$ensembl_gene_id_version)],]

genecount <- genecount[rownames(genecount) %in% genes.left$ensembl_gene_id_version,]

genes.left <- genes.left[match(rownames(genecount), genes.left$ensembl_gene_id_version),]
# all(genes.left$ensembl_gene_id_version == rownames(genecount))
# rownames(genecount) <- genes.left$hgnc_symbol

genecount <- apply(as.matrix(genecount), 2, as.numeric)
rownames(genecount) <- genes.left$hgnc_symbol
lemay.raw <- as.data.frame(genecount)

rm(genes, genes.left, df, geneid, filepath, genecount)
```

## Normalization
Raw count matrix: lemay.raw
Normailzed count matrix: lemay.cpm
```{r}
y <- DGEList(lemay.raw)
y <- calcNormFactors(y, method = "TMM")
lemay.cpm <- cpm(y, log=TRUE, prior.count = 1)

rm(y)
```

# Preprocess Kelsey dataset
TPM count instead of raw counts were used later in scissor
Fat content in metadata was re-categorized into high fat and low fat to create phenotype labels

## TPM counts were directly downloaded and gene ID was converted into gene symbols
```{r}
kelsey.tpm <- read.csv(file="R:/HBMSC2022-A7264/51_MFG_draft/datasets/kelsey/human_milk_geneExpr_TPM.csv")
geneID <- kelsey.tpm$X
# options(timeout=10000)
genes <- getBM(attributes = c('ensembl_gene_id_version', 'hgnc_symbol'),
               filters = 'ensembl_gene_id_version',
               values = geneID,
               mart = useEnsembl(biomart = "genes",
                                 dataset = "hsapiens_gene_ensembl",
                                 version = 110))
genes <- genes[genes$hgnc_symbol!="",]
# length(unique(genes$hgnc_symbol))
genes.left <- genes[!genes$hgnc_symbol %in% genes$hgnc_symbol[duplicated(genes$hgnc_symbol)],]
genes.left <- genes.left[!genes.left$ensembl_gene_id_version %in% genes$ensembl_gene_id_version[duplicated(genes$ensembl_gene_id_version)],]
kelsey.tpm <- kelsey.tpm[kelsey.tpm$X %in% genes.left$ensembl_gene_id_version,]
genes.left <- genes.left[match(kelsey.tpm$X, genes.left$ensembl_gene_id_version),]
# all(genes.left$ensembl_gene_id_version == kelsey.tpm$X)
kelsey.tpm <- kelsey.tpm[,-1]
kelsey.tpm <- apply(kelsey.tpm, 2, as.numeric)
rownames(kelsey.tpm) <- genes.left$hgnc_symbol
kelsey.tpm <- as.data.frame(kelsey.tpm)

rm(genes, geneID, genes.left)
```

## Recategorize samples into different fat groups

downsampling by fat content record;
filter out lowly expressing genes to downsize the data;
set the hat- vs low- fat threshold
categorize the samples by their fat content: high- and low- phenotype

```{r}
kelsey.meta <- read.delim(file="R:/HBMSC2022-A7264/51_MFG_draft/datasets/kelsey/milk_sample_metadata.tsv")
kelsey.meta <- kelsey.meta[!is.na(kelsey.meta$fat1),]

kelsey.tpm <- kelsey.tpm[, intersect(colnames(kelsey.tpm),kelsey.meta$study_id)]
kelsey.meta <- kelsey.meta[kelsey.meta$study_id %in% intersect(colnames(kelsey.tpm),kelsey.meta$study_id),] 
kelsey.tpm <- kelsey.tpm[,match(kelsey.meta$study_id, colnames(kelsey.tpm))]
# all(colnames(kelsey.tpm)==kelsey.meta$study_id)

filtered <- edgeR::filterByExpr(kelsey.tpm, min.prop = 0.5)
kelsey.tpm <- kelsey.tpm[filtered,]
rm(filtered)

summary(kelsey.meta$fat1)

# ggplot(kelsey.meta, aes(x=fat1)) + geom_density() + theme_bw()

kelsey.meta$fatLevel[kelsey.meta$fat1 < 4.023] <- "Low"
kelsey.meta$fatLevel[kelsey.meta$fat1 > 5.598] <- "High" # 5.598, not 5.496
kelsey.meta$fatLevel1[kelsey.meta$fatLevel == "Low"] <- 0
kelsey.meta$fatLevel1[kelsey.meta$fatLevel == "High"] <- 1

kelsey.meta <- kelsey.meta[!is.na(kelsey.meta$fatLevel),]
kelsey.tpm <- kelsey.tpm[,kelsey.meta$study_id]
all(colnames(kelsey.tpm)==kelsey.meta$study_id)

kelsey.tag <- c("Low", "High")
```

# Preprocess Twigger dataset
keep only LC2, subset from the integrated dataset (Twigger+Nyquist)
what are removed: cycling cells, basal cells, LC1
```{r}
# twigger <- readRDS("R:/HBMSC2022-A7264/51_MFG_draft/datasets/twigger/twigger_0506.rds")
# twigger <- twigger[,twigger$Stromal.clusters=="Epithelial"]

epi <- readRDS("R:/HBMSC2022-A7264/51_MFG_draft/datasets/twigger/epi.rds")
epi <- CreateSeuratObject(counts=epi[['RNA']]$counts, meta.data = epi@meta.data[, c("Source", "Individual", "Age","Infant_age", "percent.mt", "batch", "Parity", "bm_cell_type", "hpca.main")])
epi <- subset(epi, subset=batch != "batch0")

epi[["RNA"]] <- split(epi[["RNA"]], f = epi$batch)

options(future.globals.maxSize = 8000 * 1024^2)
epi <- SCTransform(epi, vst.flavor = "v2") %>%
  RunPCA() %>%
  IntegrateLayers(method = HarmonyIntegration,
                  orig.reduction = "pca", new.reduction = "harmony") %>%
  FindNeighbors(dims = 1:30, reduction = "pca") %>%
  FindClusters(resolution = 0.5) %>%
  RunUMAP(reduction = "harmony", dims = 1:35)   

epi <- subset(epi, subset = bm_cell_type=="LC2")
# length(intersect(colnames(epi)[epi$bm_cell_type=="LC2"], colnames(twigger)[twigger$Epithelial.clusters=="Luminal_HMC2"]))

twigger <- epi
rm(epi)

twigger@meta.data$processing[twigger@meta.data$Source %in% c("LMC1", "LMC2B", "LMC3", "LMC4", "LMC9")] <- "Fresh"
twigger@meta.data$processing[twigger@meta.data$Source %in% c("LMC2", "LMC5", "LMC6", "LMC7", "LMC8")] <- "Frozen"

```

# Biological assumptions applied in computation

## Selection 1:
MFG events will have these characteristics:
  Feature counts < 2000
  Ribosomal gene expression percentage > 20%
  Mitochondrial gene expression percentage < 5%
```{r}
twigger[["percent.rb"]] <- PercentageFeatureSet(twigger, pattern = "^RP[SL]")
twigger@meta.data <- twigger@meta.data %>% mutate(selection1 = case_when(
  percent.rb > 20 & nFeature_RNA < 2000 & percent.mt < 5 ~ "MFG",
  .default = "Cell"))

summary(twigger$percent.rb)
summary(twigger$percent.rb[twigger$processing=="Fresh"])
summary(twigger$percent.rb[twigger$processing=="Frozen"])
VlnPlot(twigger, group.by = "processing", features = "percent.rb", pt.size = 0) + 
  geom_boxplot(width = 0.1, outliers = FALSE)

summary(twigger$percent.mt)
summary(twigger$percent.mt[twigger$processing=="Fresh"])
summary(twigger$percent.mt[twigger$processing=="Frozen"])
VlnPlot(twigger, group.by = "processing", features = "percent.mt", pt.size = 0) + 
  geom_boxplot(width = 0.1, outliers = FALSE)

table(twigger$selection1, twigger$Source)
table(twigger$selection1, twigger$processing)

FeatureScatter(twigger, feature1 = "percent.mt", feature2 = "percent.rb", group.by = "processing") + 
  geom_hline(yintercept = 20, color = "blue", linetype = "dashed") +
  geom_vline(xintercept = 5, color = "blue", linetype = "dashed")

# load("R:/HBMSC2022-A7264/51_MFG_draft/27Mar2026.RData")

```
## Selection 2:

Transcriptome similarity between Twigger and Lemay
  across ribosomal genes as main test

### Scale the Twigger and Lemay count matrix
```{r}
tw.fresh <- subset(twigger, subset = processing == "Fresh")
tw.frozen <- subset(twigger, subset = processing == "Frozen")

tw.fresh <- tw.fresh[["SCT"]]$data
tw.frozen <- tw.frozen[["SCT"]]$data

ribogenes <- grep("^RP[SL]", rownames(twigger), value=TRUE)

tw.fresh <- tw.fresh[Matrix::rowSums(tw.fresh) > 0,]
tw.frozen <- tw.frozen[Matrix::rowSums(tw.frozen) > 0,]
lemay <- lemay.cpm[Matrix::rowSums(lemay.cpm) > 0,]

tw.fresh <- tw.fresh[intersect(ribogenes, rownames(lemay)),]
tw.frozen <- tw.frozen[intersect(ribogenes, rownames(lemay)),]
lemay <- lemay[intersect(ribogenes, rownames(lemay)),]

merged.matrix <- cbind(lemay, tw.fresh, tw.frozen)
merged.matrix.scaled <- t(scale(t(merged.matrix)))

```

### Euclidean distance between individual Lemay sample and Twigger events across ribosomal genes
```{r}
lemay.scaled <- merged.matrix.scaled[,1:4]
tw.fresh.scaled <- merged.matrix.scaled[,5:(ncol(tw.fresh)+4)]
tw.frozen.scaled <- merged.matrix.scaled[,(ncol(tw.fresh)+4+1):(ncol(tw.frozen)+ncol(tw.fresh)+4)]

dist_lemay_fresh <- rdist::cdist(t(lemay.scaled), t(tw.fresh.scaled), metric="euclidean")
dist_lemay_fresh <- as.matrix(dist_lemay_fresh)
colnames(dist_lemay_fresh) <- colnames(tw.fresh.scaled)
rownames(dist_lemay_fresh) <- colnames(lemay.scaled)

dist_lemay_frozen <- rdist::cdist(t(lemay.scaled), t(tw.frozen.scaled), metric="euclidean")
dist_lemay_frozen <- as.matrix(dist_lemay_frozen)
colnames(dist_lemay_frozen) <- colnames(tw.frozen.scaled)
rownames(dist_lemay_frozen) <- colnames(lemay.scaled)


df <- data.frame(process=c(rep("Fresh", 4*ncol(dist_lemay_fresh)), 
                           rep("Frozen", 4*ncol(dist_lemay_frozen))),
                 dist=c(dist_lemay_fresh[1,],
                        dist_lemay_fresh[2,],
                        dist_lemay_fresh[3,],
                        dist_lemay_fresh[4,],
                        dist_lemay_frozen[1,],
                        dist_lemay_frozen[2,],
                        dist_lemay_frozen[3,],
                        dist_lemay_frozen[4,]),
                 LemaySample=c(rep("Lemay_s1", ncol(dist_lemay_fresh)),
                               rep("Lemay_s2", ncol(dist_lemay_fresh)),
                               rep("Lemay_s3", ncol(dist_lemay_fresh)),
                               rep("Lemay_s4", ncol(dist_lemay_fresh)),
                               rep("Lemay_s1", ncol(dist_lemay_frozen)),
                               rep("Lemay_s2", ncol(dist_lemay_frozen)),
                               rep("Lemay_s3", ncol(dist_lemay_frozen)),
                               rep("Lemay_s4", ncol(dist_lemay_frozen))))

ggplot(df, aes(x=dist, fill=process)) +
  geom_density(alpha=0.5, position="identity") +
  theme_bw() +
  geom_vline(data=plyr::ddply(df, c("process", "LemaySample"), 
                              summarise, 
                              grp.mean=mean(dist)), 
             aes(xintercept=grp.mean, color=process),
             linetype="dashed") +
  facet_wrap(~LemaySample)

```

### Cluster the events in fresh samples based on their distance to Lemay samples

```{r}
class_mclust <- data.frame(cells = colnames(dist_lemay_fresh))

i=1 # 1, 2, 3, 4
data <- dist_lemay_fresh[i,] 
BIC <- mclustBIC(data,G=2)
mod1 <- Mclust(data, x = BIC)
class_mclust <- cbind(class_mclust, mod1$classification)

i=2 # 1, 2, 3, 4
data <- dist_lemay_fresh[i,] 
BIC <- mclustBIC(data,G=2)
mod1 <- Mclust(data, x = BIC)
class_mclust <- cbind(class_mclust, mod1$classification)

i=3 # 1, 2, 3, 4
data <- dist_lemay_fresh[i,] 
BIC <- mclustBIC(data,G=2)
mod1 <- Mclust(data, x = BIC)
class_mclust <- cbind(class_mclust, mod1$classification)

i=4 # 1, 2, 3, 4
data <- dist_lemay_fresh[i,] 
BIC <- mclustBIC(data,G=2)
mod1 <- Mclust(data, x = BIC)
class_mclust <- cbind(class_mclust, mod1$classification)
  
rm(i, data, BIC, mod1)

class_mclust <- class_mclust[,2:ncol(class_mclust)]
colnames(class_mclust) <- paste0("Lemay", 1:4)

class_mclust$final <- rowSums(class_mclust)

class_mclust <- class_mclust %>% mutate(Group = case_when(final == 4 ~ "MFG",
                                                          .default = "Cell"))

# keeping df and class_mclust just in case
temp <- df[df$process=="Fresh",]
temp$Group <- rep(class_mclust$Group, times=4)

ggplot(temp, aes(x=dist, fill=Group)) +
  geom_density(alpha=0.5, position="identity") +
  theme_bw() +
  geom_vline(data=plyr::ddply(temp, c("Group", "LemaySample"),
                              summarise,
                              grp.mean=mean(dist)),
             aes(xintercept=grp.mean),
             linetype="dashed") +
  facet_wrap(~LemaySample) +
  scale_fill_manual(values=c("grey", "#FFFF00"))

twigger@meta.data <- twigger@meta.data %>% mutate(selection2 = case_when(
  colnames(twigger) %in% rownames(class_mclust)[class_mclust$Group=="MFG"] ~ "MFG",
  .default = "Cell"
))

table(twigger$processing, twigger$selection2)
rm(tw.fresh, tw.frozen, merged.matrix, merged.matrix.scaled, ribogenes, lemay, lemay.scaled, tw.fresh.scaled, tw.frozen.scaled, dist_lemay_fresh, dist_lemay_frozen)
rm(temp)
```


## Selection 3:

Kelsey sample fat level phenotype label transferring with scissor
```{r}
b1 <- subset(twigger, subset=batch=="batch1")
b2 <- subset(twigger, subset=batch=="batch2")
b3 <- subset(twigger, subset=batch=="batch3")

DefaultAssay(b1) <- "RNA"
DefaultAssay(b2) <- "RNA"
DefaultAssay(b3) <- "RNA"

b1 <- b1 %>% 
  JoinLayers() %>%
  GetAssay() %>%
  CreateSeuratObject() %>%
  NormalizeData() %>%
  FindVariableFeatures(selection.method = "vst", nfeatures = 2000) %>%
  ScaleData(features = rownames(.)) %>%
  RunPCA(features = VariableFeatures(.)) %>%
  FindNeighbors(dims = 1:25) %>%
  FindClusters(resolution = 0.5) %>%
  RunUMAP(dims = 1:25)
b1[["RNA"]] <- as(object = b1[["RNA"]], Class = "Assay")  

b2 <- b2 %>% 
  JoinLayers() %>%
  GetAssay() %>%
  CreateSeuratObject() %>%
  NormalizeData() %>%
  FindVariableFeatures(selection.method = "vst", nfeatures = 2000) %>%
  ScaleData(features = rownames(.)) %>%
  RunPCA(features = VariableFeatures(.)) %>%
  FindNeighbors(dims = 1:25) %>%
  FindClusters(resolution = 0.5) %>%
  RunUMAP(dims = 1:25)
b2[["RNA"]] <- as(object = b2[["RNA"]], Class = "Assay") 

b3 <- b3 %>% 
  JoinLayers() %>%
  GetAssay() %>%
  CreateSeuratObject() %>%
  NormalizeData() %>%
  FindVariableFeatures(selection.method = "vst", nfeatures = 2000) %>%
  ScaleData(features = rownames(.)) %>%
  RunPCA(features = VariableFeatures(.)) %>%
  FindNeighbors(dims = 1:25) %>%
  FindClusters(resolution = 0.5) %>%
  RunUMAP(dims = 1:25)
b3[["RNA"]] <- as(object = b3[["RNA"]], Class = "Assay")

infos1 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b1, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.2, family = "binomial", Save_file = "R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff2/Scissor_1.RData")

infos2 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b2, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.2, family = "binomial", Save_file = "R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff2/Scissor_2.RData")

infos3 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b3, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.2, family = "binomial", Save_file = "R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff2/Scissor_3.RData")

save(infos1, infos2, infos3, file = "R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff2/three_batches.RData")

Scissor_select <- rep(0, ncol(b1))
names(Scissor_select) <- colnames(b1)
Scissor_select[infos1$Scissor_pos] <- 1
Scissor_select[infos1$Scissor_neg] <- 2
b1_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b2))
names(Scissor_select) <- colnames(b2)
Scissor_select[infos2$Scissor_pos] <- 1
Scissor_select[infos2$Scissor_neg] <- 2
b2_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b3))
names(Scissor_select) <- colnames(b3)
Scissor_select[infos3$Scissor_pos] <- 1
Scissor_select[infos3$Scissor_neg] <- 2
b3_scissor <- Scissor_select

scissor_result <- c(b1_scissor, b2_scissor, b3_scissor)
meta <- scissor_result[order(match(scissor_result,colnames(twigger)))]

twigger <- AddMetaData(twigger, metadata = meta, col.name = "scissor_batch_0.2")

```

scissor on HPC, testing different cutoff: 0.4, 0.6, 0.8
```{r}
# save(b1, b2, b3, kelsey.tpm, kelsey.meta, kelsey.tag, file="R:/HBMSC2022-A7264/51_MFG_draft/scissor/mfg_draft_scissor_hpc.RData")

infos1 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b1, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.4, family = "binomial", Save_file = "cutoff4/Scissor_1.RData")
infos2 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b2, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.4, family = "binomial", Save_file = "cutoff4/Scissor_2.RData")
infos3 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b3, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.4, family = "binomial", Save_file = "cutoff4/Scissor_3.RData")

save(infos1, infos2, infos3, file="cutoff4/three_batches.RData")
load("R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff4/three_batches.RData")

Scissor_select <- rep(0, ncol(b1))
names(Scissor_select) <- colnames(b1)
Scissor_select[infos1$Scissor_pos] <- 1
Scissor_select[infos1$Scissor_neg] <- 2
b1_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b2))
names(Scissor_select) <- colnames(b2)
Scissor_select[infos2$Scissor_pos] <- 1
Scissor_select[infos2$Scissor_neg] <- 2
b2_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b3))
names(Scissor_select) <- colnames(b3)
Scissor_select[infos3$Scissor_pos] <- 1
Scissor_select[infos3$Scissor_neg] <- 2
b3_scissor <- Scissor_select

scissor_result <- c(b1_scissor, b2_scissor, b3_scissor)
meta <- scissor_result[order(match(scissor_result,colnames(twigger)))]

twigger <- AddMetaData(twigger, metadata = meta, col.name = "scissor_batch_0.4")





infos1 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b1, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.6, family = "binomial", Save_file = "cutoff6/Scissor_1.RData")
infos2 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b2, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.6, family = "binomial", Save_file = "cutoff6/Scissor_2.RData")
infos3 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b3, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.6, family = "binomial", Save_file = "cutoff6/Scissor_3.RData")

save(infos1, infos2, infos3, file="cutoff6/three_batches.RData")
load("R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff6/three_batches.RData")

Scissor_select <- rep(0, ncol(b1))
names(Scissor_select) <- colnames(b1)
Scissor_select[infos1$Scissor_pos] <- 1
Scissor_select[infos1$Scissor_neg] <- 2
b1_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b2))
names(Scissor_select) <- colnames(b2)
Scissor_select[infos2$Scissor_pos] <- 1
Scissor_select[infos2$Scissor_neg] <- 2
b2_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b3))
names(Scissor_select) <- colnames(b3)
Scissor_select[infos3$Scissor_pos] <- 1
Scissor_select[infos3$Scissor_neg] <- 2
b3_scissor <- Scissor_select

scissor_result <- c(b1_scissor, b2_scissor, b3_scissor)
meta <- scissor_result[order(match(scissor_result,colnames(twigger)))]

twigger <- AddMetaData(twigger, metadata = meta, col.name = "scissor_batch_0.6")

infos1 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b1, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.8, family = "binomial", Save_file = "cutoff8/Scissor_1.RData")
infos2 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b2, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.8, family = "binomial", Save_file = "cutoff8/Scissor_2.RData")
infos3 <- Scissor(bulk_dataset = as.matrix(kelsey.tpm), sc_dataset = b3, kelsey.meta$fatLevel1, tag = kelsey.tag, alpha = NULL, cutoff = 0.8, family = "binomial", Save_file = "cutoff8/Scissor_3.RData")

save(infos1, infos2, infos3, file="cutoff8/three_batches.RData")
load("R:/HBMSC2022-A7264/51_MFG_draft/scissor/cutoff8/three_batches.RData")

Scissor_select <- rep(0, ncol(b1))
names(Scissor_select) <- colnames(b1)
Scissor_select[infos1$Scissor_pos] <- 1
Scissor_select[infos1$Scissor_neg] <- 2
b1_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b2))
names(Scissor_select) <- colnames(b2)
Scissor_select[infos2$Scissor_pos] <- 1
Scissor_select[infos2$Scissor_neg] <- 2
b2_scissor <- Scissor_select

Scissor_select <- rep(0, ncol(b3))
names(Scissor_select) <- colnames(b3)
Scissor_select[infos3$Scissor_pos] <- 1
Scissor_select[infos3$Scissor_neg] <- 2
b3_scissor <- Scissor_select

scissor_result <- c(b1_scissor, b2_scissor, b3_scissor)
meta <- scissor_result[order(match(scissor_result,colnames(twigger)))]

twigger <- AddMetaData(twigger, metadata = meta, col.name = "scissor_batch_0.8")
```

check and compare the results from different cutoff parameters
```{r}
rm(meta, scissor_result, Scissor_select, b3_scissor, b2_scissor, b1_scissor, infos1, infos2, infos3)
# rm(b1, b2, b3)

DimPlot(twigger, reduction = 'umap', group.by = 'scissor_batch_0.2', cols = c('grey','indianred1','royalblue'), pt.size = 1.2, order = c(2, 1))

DimPlot(twigger, reduction = 'umap', group.by = 'scissor_batch_0.4', cols = c('grey','indianred1','royalblue'), pt.size = 1.2, order = c(2, 1))

DimPlot(twigger, reduction = 'umap', group.by = 'scissor_batch_0.6', cols = c('grey','indianred1','royalblue'), pt.size = 1.2, order = c(2, 1))

DimPlot(twigger, reduction = 'umap', group.by = 'scissor_batch_0.8', cols = c('grey','indianred1','royalblue'), pt.size = 1.2, order = c(2, 1))

```

```{r}
rm(b1, b2, b3)
```


cutoff=0.6 was used
```{r}
twigger$selection3 <- "Cell"
twigger$selection3[twigger$scissor_batch_0.6==1] <- "MFG"
table(twigger$selection3, twigger$processing)
```


## Majority vote of three selection methods

Venn plot to visualize the label results
```{r}
library(ggVennDiagram)
ggVennDiagram(list(Selection1 = colnames(twigger)[twigger$selection1=="MFG"],
                   Selection2 = colnames(twigger)[twigger$selection2=="MFG"],
                   Selection3 = colnames(twigger)[twigger$selection3=="MFG"]),
              set_size = 6, label_size = 9) +
  scale_fill_gradient(low = "#F4FAFE", high = "#4981BF") +
  theme(legend.position = "none")
```

majority voting
```{r}
twigger$final_decision <- "Cell"
twigger$final_decision[twigger$selection1=="MFG" & twigger$selection2=="MFG" & twigger$selection3=="MFG"] <- "MFG"
table(twigger$final_decision)
```
## MFG specific gene set

re-normalize and batch correct (integrate) the data for LC2 cells
```{r}
twigger.lc2.re <- twigger
DefaultAssay(twigger.lc2.re) <- "RNA"

twigger.lc2.re <- JoinLayers(twigger.lc2.re) %>%
  split(f = .$batch) %>%
  SCTransform() %>%
  RunPCA(assay = "SCT") %>%
  RunUMAP(dims = 1:25, assay = "SCT") %>%
  FindNeighbors(dims = 1:25) %>%
  FindClusters(resolution = 0.8) %>%
  IntegrateLayers(method = HarmonyIntegration,
                  orig.reduction = "pca",
                  verbose = FALSE) %>%
  FindNeighbors(reduction = "harmony", dims = 1:25, assay = "SCT") %>%
  FindClusters(resolution = 0.3) %>%
  RunUMAP(reduction = "harmony", dims = 1:25, assay = "SCT")

twigger.lc2.re <- PrepSCTFindMarkers(twigger.lc2.re)

```

downsample and determine the cell group representation for DE analysis
- cells were labeled as Cell in Selection 1 and from fresh samples were used as cell pool for sampling

```{r}
mfg.barcode <- colnames(twigger.lc2.re)[twigger.lc2.re$final_decision=="MFG"]
cell.bracode <- colnames(twigger.lc2.re)[twigger.lc2.re$selection1=="Cell"&twigger.lc2.re$processing=="Fresh"]
```

Available probe sets in Lifeblood dataset
```{r}
avail_probeset <- read.csv("R:/HBMSC2022-A7264/51_MFG_draft/datasets/lifeblood/Chromium_Human_Transcriptome_Probe_Set_v1.0.1_GRCh38-2020-A.csv",header = TRUE, skip=5)
avail_probeset <- avail_probeset$probe_id
avail_probeset <- stringr::str_match(avail_probeset, "\\|\\s*(.*?)\\s*\\|")[,2]
avail_probeset <- unique(avail_probeset)

```

- repeat 5 times and select the common DEGs
```{r}
marker.list <- lapply(1:5, function(i){
  seed.pool <- c(233, 234, 235, 236, 237)
  set.seed(seed.pool[i])
  cell.sub <- sample(cell.bracode, size = length(mfg.barcode), replace=F)
  
  temp <- twigger.lc2.re
  temp$de <- "background"
  temp$de[colnames(temp) %in% mfg.barcode] <- "mfg"
  temp$de[colnames(temp) %in% cell.sub] <- "cell"
  Idents(temp) <- "de"
  
  mfg.marker <- FindMarkers(temp, 
                            ident.1 = "mfg",
                            ident.2 = "cell",
                            test.use = "wilcox")
  mfg.marker <- mfg.marker %>% filter(p_val_adj < 0.05)
  return(mfg.marker)
})

sapply(marker.list, nrow)
sapply(marker.list, function(dataframe){
  table(dataframe$avg_log2FC>0)
})

geneset_up_threshold.list <- lapply(c(0, 0.5, 1, 1.5, 2), function(i){
  Reduce(intersect, lapply(marker.list, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC>i]}))
})

geneset_down_threshold.list <- lapply(c(0, -0.5, -1, -1.5, -2), function(i){
  Reduce(intersect, lapply(marker.list, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC<i]}))
})

```


repeat 10 times (just for testing and results won't be further taken)
```{r}
marker.list.10 <- lapply(1:10, function(i){
  seed.pool <- c(233, 234, 235, 236, 237, 238, 239, 240, 241, 242)
  set.seed(seed.pool[i])
  cell.sub <- sample(cell.bracode, size = length(mfg.barcode), replace=F)
  
  temp <- twigger.lc2.re
  temp$de <- "background"
  temp$de[colnames(temp) %in% mfg.barcode] <- "mfg"
  temp$de[colnames(temp) %in% cell.sub] <- "cell"
  Idents(temp) <- "de"
  
  mfg.marker <- FindMarkers(temp, 
                            ident.1 = "mfg",
                            ident.2 = "cell",
                            test.use = "wilcox")
  mfg.marker <- mfg.marker %>% filter(p_val_adj < 0.05)
  return(mfg.marker)
})

sapply(marker.list.10, nrow)
sapply(marker.list.10, function(dataframe){
  table(dataframe$avg_log2FC>0)
})

geneset_up_threshold.list.10 <- lapply(c(0, 0.5, 1, 1.5, 2), function(i){
  Reduce(intersect, lapply(marker.list.10, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC>i]}))
})

geneset_down_threshold.list.10 <- lapply(c(0, -0.5, -1, -1.5, -2), function(i){
  Reduce(intersect, lapply(marker.list.10, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC<i]}))
})
```

```{r}

common.de.all.list <- lapply(list(geneset_up_threshold.list, 
         geneset_down_threshold.list,
         geneset_up_threshold.list.10,
         geneset_down_threshold.list.10), function(list){
  sapply(list, function(i){
  intersect(i, avail_probeset)
}) 
})

lapply(common.de.all.list, lengths)

# common.de.all.list variable includes:
# [[1]] common DE over repeat = 5 and probes, UP in MFG, across 5 LC
# [[2]] common DE over repeat = 5 and probes, DOWN in MFG, across 5 LC
# [[3]] common DE over repeat = 10 and probes, UP in MFG, across 5 LC
# [[4]] common DE over repeat = 10 and probes, DOWN in MFG, across 5 LC
rm(avail_probeset)
```

save image

Decide to use 5 repeats and 1.5 log2FC cutoff

```{r}
mfg.positive <- common.de.all.list[[1]][[4]]
mfg.negative <- common.de.all.list[[2]][[4]]
cat(mfg.positive, sep = ", ")
cat(mfg.negative, sep = ", ")
# oldset <- readRDS(file="R:/HBMSC2022-A7264/48_RedCross_samples/07_scissor/geneSets.rds")
```

a different visualization for DE marker counts
```{r}

de.counts <- data.frame(counts=unlist(lapply(common.de.all.list, lengths)),
                        sd=xxx,
                        iteration=factor(c(rep("iteration5", 10), 
                                           rep("iteration10", 10)), 
                                         levels = c("iteration5", "iteration10")),
                        threshold=rep(factor(c(0,0.5, 1, 1.5, 2)), 4),
                        direction=factor(rep(c("Up", "Down", "Up", "Down"), 
                                             each=5), 
                                         levels = c("Up", "Down")))
de.counts %>% 
  ggplot(aes(x=threshold, y=counts, colour = direction, group = interaction(direction, iteration))) +
  geom_line(aes(linetype = iteration), linewidth = 1.3) +
  geom_errorbar(aes(ymin=counts-sd, ymax=counts+sd), width=.2,
                 position=position_dodge(0.05)) +
  theme_bw() +
  theme(legend.text=element_text(size=15),
        axis.title = element_text(size = 15))
  

```

A line plot that doesn't exclude non-probe genes
```{r}
geneset_up_all_threshold.list.10 <- lapply(c(0, 0.5, 1, 1.5, 2), function(i){
  lapply(marker.list.10, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC>i]})
})

geneset_down_all_threshold.list.10 <- lapply(c(0, -0.5, -1, -1.5, -2), function(i){
  lapply(marker.list.10, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC<i]})
})

geneset_up_all_threshold.list.5 <- lapply(c(0, 0.5, 1, 1.5, 2), function(i){
  lapply(marker.list, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC>i]})
})

geneset_down_all_threshold.list.5 <- lapply(c(0, -0.5, -1, -1.5, -2), function(i){
  lapply(marker.list, function(dataframe){rownames(dataframe)[dataframe$avg_log2FC<i]})
})

sapply(geneset_up_all_threshold.list.10, lengths)
sapply(geneset_down_all_threshold.list.10, lengths)
sapply(geneset_up_all_threshold.list.5, lengths)
sapply(geneset_down_all_threshold.list.5, lengths)

apply(sapply(geneset_up_all_threshold.list.10, lengths), 2,sd)
apply(sapply(geneset_down_all_threshold.list.10, lengths), 2,sd)
apply(sapply(geneset_up_all_threshold.list.5, lengths), 2,sd)
apply(sapply(geneset_down_all_threshold.list.5, lengths), 2,sd)

apply(sapply(geneset_up_all_threshold.list.10, lengths), 2,mean)
apply(sapply(geneset_down_all_threshold.list.10, lengths), 2,mean)
apply(sapply(geneset_up_all_threshold.list.5, lengths), 2,mean)
apply(sapply(geneset_down_all_threshold.list.5, lengths), 2,mean)

# unlist(lapply(list(geneset_up_threshold.list, 
#          geneset_down_threshold.list,
#          geneset_up_threshold.list.10,
#          geneset_down_threshold.list.10), lengths))

# common.de.inclusive.list <- list(geneset_up_threshold.list, 
#          geneset_down_threshold.list,
#          geneset_up_threshold.list.10,
#          geneset_down_threshold.list.10)


de.inclusive.counts <- data.frame(counts=c(apply(sapply(geneset_up_all_threshold.list.5, lengths), 2,mean),
                                            apply(sapply(geneset_down_all_threshold.list.5, lengths), 2,mean),
                                            apply(sapply(geneset_up_all_threshold.list.10, lengths), 2,mean),
                                            apply(sapply(geneset_down_all_threshold.list.10, lengths), 2,mean)),
                        sd=c(apply(sapply(geneset_up_all_threshold.list.5, lengths), 2,sd),
                             apply(sapply(geneset_down_all_threshold.list.5, lengths), 2,sd),
                             apply(sapply(geneset_up_all_threshold.list.10, lengths), 2,sd),
                             apply(sapply(geneset_down_all_threshold.list.10, lengths), 2,sd)),
                        iteration=factor(c(rep("iteration5", 10), 
                                           rep("iteration10", 10)), 
                                         levels = c("iteration5", "iteration10")),
                        threshold=rep(factor(c(0,0.5, 1, 1.5, 2)), 4),
                        direction=factor(rep(c("Up", "Down", "Up", "Down"), 
                                             each=5), 
                                         levels = c("Up", "Down")))
de.inclusive.counts %>% 
  ggplot(aes(x=threshold, y=counts, colour = direction, group = interaction(direction, iteration))) +
  geom_line(aes(linetype = iteration), linewidth = 1.5) +
  geom_errorbar(aes(ymin=counts-sd, ymax=counts+sd), width=.2,
                 position=position_dodge(0.05)) +
  theme_bw() +
  # labs(title = "All DE genes including non-probeset genes and without common gene subset step")+
  theme(legend.text=element_text(size=20),
        axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20))



```


verify #11 comment
```{r}
up_i5_1.5_common <- common.de.all.list[[1]][[4]]
up_i10_1.5_common <- common.de.all.list[[3]][[4]]

down_i5_1.5_common <- common.de.all.list[[2]][[4]]
down_i10_1.5_common <- common.de.all.list[[4]][[4]]

library(VennDiagram)

venn.diagram(x = list(iteration_5 = common.de.all.list[[1]][[4]],
                      iteration_10 = common.de.all.list[[3]][[4]]), 
             disable.logging = T,
             filename = NULL,
             output = FALSE,
             fill = c(alpha('#440154ff',0.3), alpha('#fde725ff',0.3)),
             cat.col = c("#440154ff", '#fde725ff'))

venn.diagram(x = list(iteration_5 = common.de.all.list[[2]][[4]],
                      iteration_10 = common.de.all.list[[4]][[4]]), 
             disable.logging = T,
             filename = NULL,
             output = FALSE,
             fill = c(alpha('#440154ff',0.3), alpha('#fde725ff',0.3)),
             cat.col = c("#440154ff", '#fde725ff'))

```


# Verification

```{r}
library(escape)
library(ggridges)
library(forcats)
geneSets <- list(MFGposi=mfg.positive, MFGnega=mfg.negative)

```


## MFG identification in Twigger dataset
```{r}
twigger.lc2.re <- runEscape(twigger.lc2.re,
                            method = "UCell", # "AUCell"
                            gene.sets = geneSets,
                            groups = 5000,
                            min.size = NULL,
                            normalize = FALSE,
                            new.assay.name = "escape.UCell") # "escape.UCell.norm"

pp <- ridgeEnrichment(twigger.lc2.re, 
                assay = "escape.UCell",
                gene.set = "MFGposi",
                color.by = "MFGposi")

pn <- ridgeEnrichment(twigger.lc2.re, 
                assay = "escape.UCell",
                gene.set = "MFGnega",
                color.by = "MFGnega")

temp <- data.frame(difference=(pp$data$MFGposi - pn$data$MFGnega),
                   cluster=as.character(pn$data$ident),
                   process=twigger.lc2.re@meta.data$processing,
                   class=twigger.lc2.re@meta.data$final_decision)

# Idents(twigger.lc2.re) <- "seurat_clusters"

heatmapEnrichment(twigger.lc2.re,
                  assay= "escape.UCell",
                  group.by = "seurat_clusters",
                  scale=TRUE)

geyserEnrichment(twigger.lc2.re,
                 assay = "escape.UCell",
                 gene.set = "MFGposi", # "MFGnega", "MFGposi"
                 order.by = "mean") # facet.by = "processing"

DimPlot(twigger.lc2.re, group.by="seurat_clusters", split.by = "final_decision", label = T)

ggplot(temp, aes(x=difference, fill=class)) + 
  geom_density(alpha = 0.5) +
  theme_bw()

temp %>% # ridge plot
  mutate(cluster = fct_reorder(cluster, difference, .fun='mean')) %>%
  ggplot(aes(y=reorder(cluster, difference), x=difference, fill=cluster)) + 
  geom_density_ridges() +
  facet_grid("class")+ # "class", "process"
  theme_ridges() + 
  theme(legend.position = "none") +
  ylab("") +
  xlab("") 


temp %>% # violin plot
  mutate(cluster = fct_reorder(cluster, difference, .fun='mean')) %>%
  ggplot(aes(x=reorder(cluster, difference), y=difference, fill=cluster)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  theme_bw() +
  theme(legend.position = "none")

# geyser plot

temp %>% 
  mutate(cluster = fct_reorder(cluster, difference, .fun='mean'))

twigger.lc2.re$diff <- (pp$data$MFGposi - pn$data$MFGnega)
FeaturePlot(twigger.lc2.re, feature="diff")

SCpubr::do_GeyserPlot(sample = twigger.lc2.re,
                      features = "diff",
                      scale_type = "continuous",
                      order_by_mean = TRUE) # "categorical"

```

save image

## MFG indentification in lifeblood dataset

```{r}
lifeblood.epi <- readRDS("R:/HBMSC2022-A7264/51_MFG_draft/datasets/lifeblood/Lifeblood_epithelials.rds")

lifeblood.epi <- runEscape(lifeblood.epi,
                           method = "UCell",
                           gene.sets = geneSets,
                           groups = 5000,
                           min.size = 0,
                           new.assay.name = "escape.UCell")

heatmapEnrichment(lifeblood.epi,
                  assay= "escape.UCell",
                  group.by = "seurat_clusters",
                  scale=TRUE)

pp <- ridgeEnrichment(lifeblood.epi, 
                assay = "escape.UCell",
                gene.set = "MFGposi",
                order.by = "mean",
                color.by = "MFGposi") 

pn <- ridgeEnrichment(lifeblood.epi, 
                assay = "escape.UCell",
                gene.set = "MFGnega",
                order.by = "mean",
                color.by = "MFGnega")

temp <- data.frame(difference=(pp$data$MFGposi - pn$data$MFGnega),
                   cluster=as.character(pn$data$ident))

temp %>%
  mutate(cluster = fct_reorder(cluster, difference, .fun='mean')) %>%
  ggplot(aes(y=reorder(cluster, difference), x=difference, fill=cluster)) + 
    geom_density_ridges() +
    theme_ridges() + 
    theme(legend.position = "none") +
    ylab("") +
    xlab("")

temp %>%
  mutate(cluster = fct_reorder(cluster, difference, .fun='mean')) %>%
  ggplot(aes(x=reorder(cluster, difference), y=difference, fill=cluster)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  theme_bw() +
  theme(legend.position = "none")

lifeblood.epi$diff <- (pp$data$MFGposi - pn$data$MFGnega)
FeaturePlot(lifeblood.epi, feature="diff")

SCpubr::do_GeyserPlot(sample = lifeblood.epi,
                      features = "diff",
                      scale_type = "continuous") # "categorical"
```

try something new and different but not going to keep and use
```{r}
enrichment.scores <- escape.matrix(lifeblood.epi, 
                                   gene.sets = geneSets, 
                                   groups = 5000, 
                                   min.size = 0,
                                   method = "UCell")
ggplot(data = as.data.frame(enrichment.scores), 
      mapping = aes(enrichment.scores[,1], enrichment.scores[,2])) + 
  geom_point() + 
  theme_classic()
rm(enrichment.scores)
```


## MFG indentification in integrated dataset (twigger+nyquist+lifeblood)
```{r}
inte_3ds <- readRDS("R:/HBMSC2022-A7264/51_MFG_draft/datasets/integrated/twi_nyq_lifeblood/integrated_3ds_epi.rds")
inte_3ds <- runEscape(inte_3ds,
                      method = "UCell",
                      gene.sets = geneSets,
                      groups = 5000,
                      min.size = 0,
                      new.assay.name = "escape.UCell")

DimPlot(inte_3ds, label=TRUE)
DimPlot(inte_3ds, label = TRUE, split.by = "DS")

heatmapEnrichment(inte_3ds,
                  assay= "escape.UCell",
                  group.by = "seurat_clusters",
                  scale=TRUE)

pp <- ridgeEnrichment(inte_3ds, 
                assay = "escape.UCell",
                gene.set = "MFGposi",
                order.by = "mean",
                color.by = "MFGposi") 

pn <- ridgeEnrichment(inte_3ds, 
                assay = "escape.UCell",
                gene.set = "MFGnega",
                order.by = "mean",
                color.by = "MFGnega")

inte_3ds$diff <- (pp$data$MFGposi - pn$data$MFGnega)
FeaturePlot(inte_3ds, feature="diff")

SCpubr::do_GeyserPlot(sample = inte_3ds,
                      features = "diff",
                      scale_type = "continuous") # "categorical"


```


## Cross validation of MFGs in lifeblood dataset and Twigger dataset within the integrated dataset
```{r}
twigger_labels <- paste0("NC_", rownames(twigger.lc2.re@meta.data[twigger.lc2.re@meta.data$final_decision=="MFG",]))
lifeblood_cluster3 <- paste0("RED_", rownames(lifeblood.epi@meta.data[lifeblood.epi@meta.data$seurat_clusters=="3",]))
# lifeblood_cluster4 <- paste0("RED_", rownames(lifeblood.epi@meta.data[lifeblood.epi@meta.data$seurat_clusters=="4",]))

inte_3ds@meta.data$mfg <- "tbd"
inte_3ds@meta.data$mfg[rownames(inte_3ds@meta.data) %in% lifeblood_cluster3] <- "Lifeblood_cluster_3"

#save.image() # 25 April 2025
inte_3ds$CT1

twigger_cluster3 <- paste0("NC_", rownames(twigger.lc2.re@meta.data[twigger.lc2.re@meta.data$seurat_clusters=="3",]))

inte_3ds@meta.data$mfg[rownames(inte_3ds@meta.data) %in% twigger_cluster3] <- "Twigger_cluster_3"
inte_3ds@meta.data$mfg[rownames(inte_3ds@meta.data) %in% twigger_labels] <- "Twigger_MFG"

DimPlot(inte_3ds, group.by = "mfg", split.by = "DS", cols=c("#046C9A","#FAEFD1","#FCC89B", "#CB2314"))
# "#BE4D00" "#F68D2E" "#CC8A00" "#FDBE87""#FDAA63" "#FCC89B"


table(inte_3ds@meta.data[(inte_3ds$seurat_clusters==10 & inte_3ds$DS=="RedCr"),]$mfg)

data <- data.frame(table(inte_3ds@meta.data[inte_3ds$seurat_clusters==10,]$DS))
data$Var1 <- c("Twigger", "Nyquist", "Lifeblood")
ggplot(data, aes(x="", y=Freq, fill=Var1)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(values = c("#F8AFA8", "#FD6467", "#7FC0C6")) +
  theme(legend.title=element_blank(),
        legend.text=element_text(size=30))

data <- data.frame(table(inte_3ds$DS))
data$Var1 <- c("Twigger", "Nyquist", "Lifeblood")
ggplot(data, aes(x="", y=Freq, fill=Var1)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(values = c("#F8AFA8", "#FD6467", "#7FC0C6")) +
  theme(legend.title=element_blank(),
        legend.text=element_text(size=30))


mfg_3ds_lifeblood <- colnames(inte_3ds[,inte_3ds$seurat_clusters==10&inte_3ds$DS=="RedCr"])

library(ggvenn)
ggvenn(
  list(integrated=mfg_3ds_lifeblood, lifeblood=lifeblood_cluster3), 
  fill_color = c("#0073C2FF", "#EFC000FF"),
  stroke_size = 0.5, set_name_size = 4, auto_scale = T
)

```

## MFG indentification in larger integrated dataset (all five + lifeblood)
```{r}
inte_6ds_mfg_cluster12 <- readRDS("51_MFG_draft/cluster12_epi_6ds.rds")

table(inte_6ds_mfg_cluster12$dataset)
mfg_6ds_lifeblood <- subset(inte_6ds_mfg_cluster12, subset = dataset=="Lifeblood")

mfg_6ds_lifeblood <- paste0("RED_", colnames(mfg_6ds_lifeblood))

length(mfg_6ds_lifeblood)
length(lifeblood_cluster3)

data <- data.frame(table(inte_6ds_mfg_cluster12$dataset))
# data <- data %>% 
#   arrange(desc(Var1)) %>%
#   mutate(prop = Freq / sum(data$Freq) *100) %>%
#   mutate(ypos = cumsum(prop)- 0.5*prop )

ggplot(data, aes(x="", y=Freq, fill=Var1)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() +
  scale_fill_manual(values = c("#FAEFD1", "#DC863B", "#DCCB4E","#F8AFA8", "#FD6467", "#7FC0C6")) +
  theme(legend.title=element_blank(),
        legend.text=element_text(size=30))

# ggplot(data, aes(x="", y=prop, fill=Var1)) +
#   geom_bar(stat="identity", width=1, color="white") +
#   coord_polar("y", start=0) +
#   theme_void() + 
#   theme(legend.position="none") +
#   geom_text(aes(y = ypos, label = Var1), color = "white", size=6) +
#   scale_fill_brewer(palette="Set1")


library(ggvenn)
ggvenn(
  list(integrated=mfg_6ds_lifeblood, lifeblood=lifeblood_cluster3), 
  fill_color = c("#0073C2FF", "#EFC000FF"),
  stroke_size = 0.5, set_name_size = 4, auto_scale=T
)

ggvenn(
  list(integrated_3ds_cluster10_lifeblood=mfg_3ds_lifeblood, lifeblood=lifeblood_cluster3, integrated_6ds_cluster12_lifeblood=mfg_6ds_lifeblood), 
  fill_color = c("#0073C2FF", "#EFC000FF", "#CD534CFF"),
  stroke_size = 0.5, set_name_size = 4
)

SCpubr::do_GeyserPlot(sample = inte_3ds,
                      features = "diff",
                      scale_type = "continuous")

```



